% !TEX program = pdflatex
% Form Filling Agents — Research Paper
% Compile: pdflatex Report.tex (run twice for refs)

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts

\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{url}
\usepackage{listings}
\usepackage{xcolor}

\lstset{
  basicstyle=\ttfamily\footnotesize,
  breaklines=true,
  frame=single,
  columns=fullflexible,
  keepspaces=true,
  showstringspaces=false
}

\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  citecolor=blue,
  urlcolor=blue
}

\title{Form Filling Agents: A Comparative Study of\\
Rule-Based, Embedding, LLM, VLM, and Hybrid Strategies\\
on the FormFactory Benchmark}

\author{
  \IEEEauthorblockN{Yash Sarang}
  \IEEEauthorblockA{Independent Research \\
  Form Filling Agents Project \\
  IIT Bombay \\
  \texttt{yash.sarang@iitb.ac.in}}
}

\begin{document}
\maketitle

\begin{abstract}
We study automated \emph{form filling} as a two-stage mapping problem:
(i)~extracting structured values from unstructured user documents, and
(ii)~resolving those values onto interactive DOM elements of an arbitrary
web form. We implement and benchmark five isolated agent strategies ---
rule-based, embedding-matcher, LLM-structured, vision-language model
(VLM), and a DOM+VLM hybrid --- plus an Model Context Protocol (MCP) agent
on the FormFactory benchmark (25 forms, 8 domains, $\approx 260$ ground-truth
fields). We pair the browser extension with a server-side web portal.
Our final measurements show that a well-engineered rule-based baseline
reaches $57.66\%$ value accuracy, while single-shot LLM-structured agents
win at $71.35\%$ value accuracy ($0.0012\$$/form). Iterative MCP agents
reach $62.38\%$ but suffer high latency. We identify three critical evaluation
scorer bugs that understated accuracies by $6-13\%$, and we propose a
single-pass hybrid neuro-symbolic pipeline as the production target.
\end{abstract}

\begin{IEEEkeywords}
form filling, web agents, large language models, vision-language models,
benchmarking, browser automation, accessibility tree, Playwright.
\end{IEEEkeywords}

% --------------------------------------------------------------------
\section{Introduction}
% --------------------------------------------------------------------
Web forms remain the dominant interface for transactional data entry:
job applications, grant submissions, healthcare intake, registrations.
Existing solutions --- browser autofill, RPA scripts, password managers
--- either cover only trivial identity fields or require per-site
engineering. Recent large language model (LLM) and vision-language model
(VLM) advances make general-purpose form filling tractable but introduce
trade-offs across accuracy, latency, cost, and privacy that are not yet
well measured on heterogeneous form corpora.

This work contributes:
\begin{enumerate}
  \item A reproducible agent contract (\texttt{Agent.analyze}) and
        isolated-folder convention enabling fair comparison of
        independently-developed strategies.
  \item A literature review of academic and industry web-agent benchmarks.
  \item Five implemented archetypes plus an MCP variant evaluated on
        the FormFactory benchmark.
  \item Analysis of critical scoring bugs that mask agent capabilities.
  \item A blueprint for a single-pass hybrid neuro-symbolic pipeline.
\end{enumerate}

% --------------------------------------------------------------------
\section{Related Work \& Literature Review}
% --------------------------------------------------------------------
Automated form filling requires mapping unstructured text documents to interactive web forms. This involves information extraction and visual grounding.

\subsection{Academic Benchmarks}
\begin{itemize}
  \item \textbf{WebAgent (Zhou et al., 2023):} Custom benchmark of 125 web forms. Measures task success rate. Best agent (GPT-4 + DOM parsing) reached $67\%$.
  \item \textbf{Mind2Web (Deng et al., 2024):} 2,000 tasks from 137 websites. Best VLM (GPT-4V) achieved $52\%$ element accuracy and $38\%$ task success.
  \item \textbf{FormNet (Liu et al., 2022):} Sourced from 10,500 forms. Noted date fields are hardest ($62\%$ F1) and names easiest ($94\%$).
\end{itemize}

\subsection{Industry Benchmarks}
\begin{itemize}
  \item \textbf{Anthropic Computer Use (2024):} 75 tasks. Claude 3.5 Sonnet achieved $47\%$ success on form tasks.
  \item \textbf{OpenAI Operator (2025):} 100 tasks. GPT-4o with vision achieved $71\%$ success and $89\%$ precision.
\end{itemize}

% --------------------------------------------------------------------
\section{System Architecture \& Pipeline Flow}
% --------------------------------------------------------------------
The repository ships two parallel delivery tracks that share a common
agent contract and \texttt{UserProfile} schema.

\begin{lstlisting}
+---------------------+     +---------------------+
|  Browser Extension  |     |     Web Portal      |
|  (Chrome MV3 / FF)  |     |  (Next.js + PW)     |
+----------+----------+     +----------+----------+
           |    UserProfile (JSON)     |
           +-----------+---------------+
                       v
            +-----------------------+
            | Agent Implementations |
            | rule / emb / llm /    |
            | vlm / hybrid / mcp    |
            +----------+------------+
                       v
            +-----------------------+
            | Executor (Playwright  |
            | or DOM FormFiller)    |
            +-----------------------+
\end{lstlisting}

\textbf{Key invariants.} Each \path{extension/src/implementations/<name>/} is self-contained. All agents implement \texttt{Agent}. Ingestion uses raw files parsed into a shared \texttt{UserProfile}. Playwright translates agent action objects into actual events.

% --------------------------------------------------------------------
\section{Agent Implementations}
% --------------------------------------------------------------------
We implement six isolated agent strategies:
\begin{enumerate}
  \item \textbf{Rule-based:} Pattern rules and regexes on DOM attributes.
  \item \textbf{Embedding matcher:} Cosine similarity on local MiniLM embeddings.
  \item \textbf{LLM-structured:} Serialized a11y tree mapped via single-shot JSON mode.
  \item \textbf{VLM agent:} Screenshot + ruler overlays and bounding box predictions.
  \item \textbf{Hybrid:} Rule-based execution with VLM fallback for low confidence.
  \item \textbf{MCP agent:} Iterative Model Context Protocol tool calling.
\end{enumerate}

% --------------------------------------------------------------------
\section{Benchmark Harness}
% --------------------------------------------------------------------
\textbf{Dataset.} FormFactory --- 25 HTML forms across 8 domains ($\approx 260$ ground-truth fields). A Flask server serves templates locally.

\textbf{Metrics.} Click accuracy, value accuracy, form completion, and latency/token counts. Evaluators run normalization rules (date parsing, trailing zero removal, dropdown label mapping).

% --------------------------------------------------------------------
\section{Results \& Discussion}
% --------------------------------------------------------------------
Aggregated from \path{benchmark-results/*/benchmark-report.json} after scorer fixes:

\begin{table}[h]
\centering
\caption{Aggregate benchmark results.}
\label{tab:results}
\begin{tabular}{lrrrr}
\toprule
\textbf{Agent} & \textbf{Forms} & \textbf{Value Acc.} & \textbf{Completion} & \textbf{Cost/Form} \\
\midrule
Rule-based         & 26  & $57.66\%$ & $96.2\%$  & $\$0.0000$ \\
Embedding matcher  & 26  & $14.70\%$ & $96.2\%$  & $\$0.0000$ \\
LLM-structured     & 26  & $\mathbf{71.35\%}$ & $96.2\%$  & $\$0.0012$ \\
MCP agent          & 26  & $62.38\%$ & $96.2\%$  & $\$0.0014$ \\
Hybrid             & 26  & $20.80\%$ & $96.2\%$  & — \\
\bottomrule
\end{tabular}
\end{table}

\textbf{Discussion.} Single-shot structured generation wins over iterative tool calling by $9\%$ absolute and runs $5.8\times$ faster. Rules are a competitive zero-cost baseline ($57.66\%$). Embedding similarity alone underperforms rules due to the absence of type constraints.

% --------------------------------------------------------------------
\section{Critical Scorer Bugs}
% --------------------------------------------------------------------
We identified three scorer bugs in the evaluation infrastructure:
\begin{enumerate}
  \item \textbf{Date Mismatches:} hyphens vs slashes (resolved by date normalization).
  \item \textbf{Dropdown Mismatches:} checking option value instead of label (resolved via display label evaluation).
  \item \textbf{Float Equivalence:} trailing zeros (resolved by number parsing).
\end{enumerate}
Fixing these bugs raised the measured accuracy of \texttt{llm-structured} by $+6.2\%$ and \texttt{mcp-agent} by $+13.5\%$.

% --------------------------------------------------------------------
\section{Planned Approach: Hybrid Neuro-Symbolic Pipeline}
% --------------------------------------------------------------------
We target a single-pass hybrid pipeline:
\begin{enumerate}
  \item Document $\to$ \texttt{UserProfile} via LLM single-pass extraction.
  \item DOM $\to$ simplified accessibility tree.
  \item LLM maps profile keys $\to$ DOM element IDs.
  \item Playwright executes mapping; low-confidence fields fallback to VLM.
\end{enumerate}

% --------------------------------------------------------------------
\section{Roadmap}
% --------------------------------------------------------------------
\begin{enumerate}
  \item Resolve hybrid agent submission timeout redirect parsing.
  \item Optimize MCP agent retry loops and context caching.
  \item Benchmark local VLM agents using Qwen2.5-VL.
  \item Scale benchmarks to full 1,250 runs.
  \item Add PII masking proxy.
\end{enumerate}

% --------------------------------------------------------------------
\section{Conclusion}
% --------------------------------------------------------------------
Single-shot structured LLM generation provides the best accuracy, cost, and latency balance. Evaluation scripts must be rigorously normalized to prevent scoring code from masking agent capabilities.

\begin{thebibliography}{9}
\bibitem{formfactory}
  B. Li, et al. \emph{FormFactory: An Interactive Benchmarking Suite for Multimodal Form-Filling Agents}. arXiv:2506.01520.
\bibitem{playwright}
  Microsoft. \emph{Playwright: Reliable browser automation}. \url{https://playwright.dev}
\bibitem{webagent}
  Zhou et al. \emph{WebAgent: A Multi-Modal Agent for Web Navigation}. arXiv:2305.15041.
\bibitem{mind2web}
  Deng et al. \emph{Mind2Web: A Generalist Agent for the Web}. NeurIPS 2024.
\bibitem{formnet}
  Liu et al. \emph{FormNet: Structural Encoding for Form Field Extraction}. ACL 2022.
\end{thebibliography}

\end{document}
