% !TEX program = pdflatex
% Form Filling Agents — Research Paper
% Compile: pdflatex Report.tex   (run twice for refs)
% This file is auto-regenerated alongside Report.md when major repo
% changes are detected. See scripts/update-report.sh.

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts

\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{url}
\usepackage{listings}
\usepackage{xcolor}

\lstset{
  basicstyle=\ttfamily\footnotesize,
  breaklines=true,
  frame=single,
  columns=fullflexible,
  keepspaces=true,
  showstringspaces=false
}

\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  citecolor=blue,
  urlcolor=blue
}

\title{Form Filling Agents: A Comparative Study of\\
Rule-Based, Embedding, LLM, VLM, and Hybrid Strategies\\
on the FormFactory Benchmark}

\author{
  \IEEEauthorblockN{Yash Sarang}
  \IEEEauthorblockA{Independent Research \\
  Form Filling Agents Project \\
  \texttt{github.com/...}}
}

\begin{document}
\maketitle

\begin{abstract}
We study automated \emph{form filling} as a two-stage mapping problem:
(i)~extracting structured values from unstructured user documents, and
(ii)~resolving those values onto interactive DOM elements of an arbitrary
web form. We implement and benchmark five isolated agent strategies ---
rule-based, embedding-matcher, LLM-structured, vision-language model
(VLM), and a DOM+VLM hybrid --- plus an MCP-orchestrated agent on the
FormFactory benchmark (25 forms, 8 domains, $\approx 260$ ground-truth
fields). The agents share a common \texttt{UserProfile} contract and are
deployed across two delivery surfaces: a privacy-preserving browser
extension and a server-side web portal. Current measurements show that a
well-engineered rule-based baseline reaches $57.7\%$ value accuracy,
while step-wise MCP agents collapse to $\approx 0.2\%$ without a
per-step grounding layer. We propose a single-pass hybrid
neuro-symbolic pipeline as the target end-state.
\end{abstract}

\begin{IEEEkeywords}
form filling, web agents, large language models, vision-language models,
benchmarking, browser automation, accessibility tree, Playwright.
\end{IEEEkeywords}

% --------------------------------------------------------------------
\section{Introduction}
% --------------------------------------------------------------------
Web forms remain the dominant interface for transactional data entry:
job applications, grant submissions, healthcare intake, registrations.
Existing solutions --- browser autofill, RPA scripts, password managers
--- either cover only trivial identity fields or require per-site
engineering. Recent large language model (LLM) and vision-language model
(VLM) advances make general-purpose form filling tractable but introduce
trade-offs across accuracy, latency, cost, and privacy that are not yet
well measured on heterogeneous form corpora.

This work contributes:
\begin{enumerate}
  \item A reproducible agent contract (\texttt{Agent.analyze}) and
        isolated-folder convention enabling fair comparison of
        independently-developed strategies.
  \item Five implemented archetypes plus an MCP variant evaluated on
        the FormFactory benchmark.
  \item A planned hybrid neuro-symbolic pipeline that motivates the
        web-portal track of the repository.
\end{enumerate}

% --------------------------------------------------------------------
\section{System Architecture}
% --------------------------------------------------------------------
The repository ships two parallel delivery tracks that share a common
agent contract and \texttt{UserProfile} schema.

\begin{lstlisting}
+---------------------+     +---------------------+
|  Browser Extension  |     |     Web Portal      |
|  (Chrome MV3 / FF)  |     |  (Next.js + PW)     |
+----------+----------+     +----------+----------+
           |    UserProfile (JSON)     |
           +-----------+---------------+
                       v
            +-----------------------+
            | Agent Implementations |
            | rule / emb / llm /    |
            | vlm / hybrid / mcp    |
            +----------+------------+
                       v
            +-----------------------+
            | Executor (Playwright  |
            | or DOM FormFiller)    |
            +-----------------------+
\end{lstlisting}

\textbf{Key invariants.} (a)~Each
\path{extension/src/implementations/<name>/} is self-contained and may
only import from \texttt{src/types/} and \texttt{src/utils/}; no
cross-agent coupling is permitted. (b)~Every agent implements the same
\texttt{Agent} interface. (c)~All agents are evaluated on an identical
FormFactory harness, with outputs persisted under
\path{benchmark-results/<agent>/}. (d)~\texttt{UserProfile} is the only
input contract. The extension produces it from
\texttt{pipeline/input-pipeline.ts}; the portal produces it from
\texttt{web-portal/src/parsers/document-parser.ts}.

% --------------------------------------------------------------------
\section{Agent Implementations}
% --------------------------------------------------------------------
\begin{table}[h]
\centering
\caption{Implemented agent archetypes.}
\label{tab:agents}
\begin{tabular}{@{}lll@{}}
\toprule
\textbf{Agent} & \textbf{Approach} & \textbf{Cost} \\
\midrule
Rule-based        & Regex on label/name/id          & None         \\
Embedding matcher & Cosine sim.\ (MiniLM, local)    & CPU          \\
LLM-structured    & A11y tree + JSON-schema output  & API tokens   \\
VLM agent         & Screenshot + ruler $\to$ bbox   & High API     \\
Hybrid            & Rule then VLM fallback          & Adaptive     \\
MCP agent         & Iterative tool calls (MCP)      & Very high    \\
\bottomrule
\end{tabular}
\end{table}

% --------------------------------------------------------------------
\section{Benchmark Harness}
% --------------------------------------------------------------------
\textbf{Dataset.} FormFactory --- 25 HTML forms across 8 domains
(Academic, Professional, Healthcare, Legal, Civic, Financial, Commerce,
Lifestyle), $\approx 260$ ground-truth fields.

\textbf{Serving.} A local Flask server at
\url{http://localhost:5000} exposes each template.

\textbf{Execution.} \texttt{extension/scripts/run-benchmark.ts} drives a
Playwright Chromium instance; each agent returns an
\texttt{AgentAction[]} sequence
(\texttt{type}, \texttt{click}, \texttt{select}).

\textbf{Metrics.} Click accuracy, value accuracy, form completion rate,
per-domain breakdown, per-field-type breakdown.

% --------------------------------------------------------------------
\section{Results}
% --------------------------------------------------------------------
Aggregated from \path{benchmark-results/*/benchmark-report.json}:

\begin{table}[h]
\centering
\caption{Current aggregate benchmark results.}
\label{tab:results}
\begin{tabular}{@{}lrrr@{}}
\toprule
\textbf{Agent} & \textbf{Fields} & \textbf{Value Acc.} & \textbf{Completion} \\
\midrule
Rule-based         & 259 & $\mathbf{57.66\%}$ & $57.66\%$ \\
MCP agent          & 116 & $\phantom{00}0.21\%$ & $\phantom{00}0.21\%$ \\
Embedding matcher  & --- & pending & --- \\
VLM agent          & --- & pending & --- \\
LLM-structured     & --- & pending & --- \\
Hybrid             & --- & pending & --- \\
\bottomrule
\end{tabular}
\end{table}

\textbf{Discussion.} The rule-based baseline is unexpectedly strong
because FormFactory exposes stable \texttt{name}/\texttt{id} attributes
and well-formed labels. The MCP agent's collapse is not a model failure
but an evaluation mismatch: MCP-style agents act across many turns and
frequently terminate before submission, leaving most fields
unattempted ($4/116$ in the latest run). A per-step grounding layer or
a turn budget per field is required for a fair comparison.

% --------------------------------------------------------------------
\section{Planned Approach: Hybrid Neuro-Symbolic Pipeline}
% --------------------------------------------------------------------
We target a single-pass pipeline rather than a step-wise loop:

\begin{enumerate}
  \item \textbf{Input (neural).} Document
        $\to$ \texttt{UserProfile} JSON via an LLM with a fixed schema.
  \item \textbf{DOM simplification (symbolic).} Page $\to$ minimal
        accessibility graph of interactive elements.
  \item \textbf{Semantic mapping (neural).} One LLM call maps
        \texttt{UserProfile} keys $\to$ DOM element IDs, emitting a
        strict $\{\text{fieldId}: \text{value}\}$ map.
  \item \textbf{Execution (symbolic).} Playwright (portal) or
        \texttt{FormFiller} (extension) applies the map deterministically;
        a re-snapshot pass handles conditional sub-forms.
  \item \textbf{Escalation (neural, on demand).} Unresolved or
        low-confidence fields fall back to the VLM agent with
        ruler-marked screenshots.
\end{enumerate}

This is the architecture the web-portal track
(\path{web-portal/src/{parsers,scraper,filler}/}) is being built around.
The browser extension retains the local-first, opt-in posture for users
who decline a server in the loop.

% --------------------------------------------------------------------
\section{Roadmap}
% --------------------------------------------------------------------
\begin{enumerate}
  \item Aggregate all \texttt{benchmark-results/*} into a unified
        comparison matrix.
  \item Wire the LLM-structured agent into the web-portal filler.
  \item Replace document-parser stub with real \texttt{pdf-parse} /
        \texttt{mammoth} pipelines.
  \item Add per-step grounding to the MCP agent.
  \item Add CI: headless benchmark on every PR.
  \item Live-site evaluation harness on 10 real public forms.
  \item Model proxy with PII redaction and key management.
\end{enumerate}

% --------------------------------------------------------------------
\section{Conclusion}
% --------------------------------------------------------------------
A clean, isolated-folder architecture allows independently developed
agent archetypes to be compared on identical footing. Early results
indicate that simple symbolic methods are strong baselines on
well-structured forms, while step-wise neural agents need explicit
grounding before they justify their cost. The hybrid neuro-symbolic
pipeline outlined above is the next milestone and is being built on the
web-portal track.

\section*{Reproducibility}
\begin{lstlisting}[language=bash]
# Extension
cd extension
npm install
npm run build:extension
npm run test:quick
npm run test:impl -- rule-based

# Web portal
cd web-portal
npm install
npx playwright install chromium
npm run dev
\end{lstlisting}

\section*{Acknowledgments}
Built on the FormFactory benchmark, Playwright, and the
WebExtensions API.

\begin{thebibliography}{9}
\bibitem{formfactory}
  FormFactory Benchmark Suite.
  Internal dataset; 25 forms, 8 domains, $\approx 260$ fields.

\bibitem{playwright}
  Microsoft. \emph{Playwright: Reliable end-to-end testing for modern
  web apps}. \url{https://playwright.dev}

\bibitem{som}
  Yang, J., et al.
  \emph{Set-of-Mark Prompting Unleashes Extraordinary Visual Grounding
  in GPT-4V}. arXiv:2310.11441.

\bibitem{mcp}
  Anthropic. \emph{Model Context Protocol (MCP) Specification}.
  \url{https://modelcontextprotocol.io}
\end{thebibliography}

\end{document}
